Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
update datasets

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that (perceived or measured) global sound level, are not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of sound sources which compose the scene. \ja{This argument is semantically a little tricky, since technically the low-level features already contain all this high-level information, it's just that the simple models we use to describe them fail to capture this high-level structure} It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \textit{e.g.} the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators \cite{lafayPartI}. Consequently, research in sound perception is now strongly focused the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occuring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so-called markers, suffice to reliably predict many high-level attributes.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task. 
An overview of the efforts for the latter task is provided by the DCASE2013 challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms as well as newer systems that considered the private datset for their experiments. % where most \ja{?} of scene predictions are achieved by majority voting of predictions over features. \ja{What about the other algorithms? Why are we excluding them here?}

@@

In addition, it is still challenging, with a state-of-the-art system based on feature design \ja{?} and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge). Another system, using a HOG+SVM approach \cite{rakotomamonjy2015histogram}, achieves $75\%$ and $92\%$ on the DCASE2013 and Rouen datasets, respectively. Recent advances using hierarchical classifier architectures obtain between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}. On the Rouen dataset, the state-of-the-art is currently $95\%$ \cite{bisot2016acoustic}.

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}. 
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a fivefold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

>>>>

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that (perceived or measured) global sound level, are not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of sound sources which compose the scene. It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \textit{e.g.} the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators \cite{lafayPartI}. Consequently, research in sound perception is now strongly focused the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occuring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so-called markers, suffice to reliably predict many high-level attributes.

@@

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC task. 
An overview of the efforts for the latter task is provided by the DCASE2013 challenge \cite{barchiesi2015acoustic}, held in 2013 to compare different approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms as well as newer systems that considered the private dataset for their experiments. Most of scene predictions are achieved by majority voting of predictions over features. \ja{What about the other algorithms? Why are we excluding them here?}

@@

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

In addition, it is still a challenging dataset, with a state-of-the-art system based on feature design and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieves  between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}.

%Recent advances using hierarchical classifier architectures obtain between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}. On the Rouen dataset, the state-of-the-art is currently $95\%$ \cite{bisot2016acoustic}.

The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a fivefold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.
